Meet the team

### 2025-02-04 team.qmd
minor updates

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Andrea Albert Pravin </h4>
  <p> Undergraduate thesis student </p>
  <p> BIOLOGY 4C12 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Faris Almoni </h4>
  <p> Undergraduate practicum student </p>
  <p> LIFESCI 4A03 </p>
  </div>
</div>

@@

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Shiuli Khanna </h4>
  <p> Undergraduate thesis student </p>
  <p> NEUROSCI 4L12 A/B </p>
  </div>
</div>

>>>>

<div class="team-member">
  <img src="images/andrea-albert-pravin.jpg" alt="images/andrea-albert-pravin.jpg" class="team-img">
  <div class="team-info">
  <h4> Andrea Albert Pravin </h4>
  <p> Undergraduate thesis student </p>
  <p> BIOLOGY 4C12 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/faris-almoni.jpg" alt="images/faris-almoni.jpg" class="team-img">
  <div class="team-info">
  <h4> Faris Almoni </h4>
  <p> Undergraduate practicum student </p>
  <p> LIFESCI 4A03 </p>
  </div>
</div>

@@

<div class="team-member">
  <img src="images/shiuli-khanna.jpg" alt="images/shiuli-khanna.jpg" class="team-img">
  <div class="team-info">
  <h4> Shiuli Khanna </h4>
  <p> Undergraduate thesis student </p>
  <p> NEUROSCI 4L12 A/B </p>
  </div>
</div>
